The SMT Competition 2015--2018

### 2019-03-20 2018/report/table-winners-main.tex
Use gray text font instead of * for non-competitive divisions.

    \wc ABVFP        &                          &                           &                                & \cc{cvc4} {CVC4} *        \\

@@

    \wc AUFBVDTLIA   &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4} *        \\
    \wc AUFDTLIA     &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4}          \\

@@

    \wc AUFNIRA      & \cc{cvc4} {CVC4} *       & {Vampire}                 & {Vampire}                      & \cc{cvc4} {CVC4}          \\

@@

    \wc BV           & \cc{cvc4} CVC4 \nc{Z3} * & {Q3B}                     & Q3B \nc{Z3}                    &  \cc{cvc4} {CVC4}         \\
    \wc BVFP         &                          &                           &                                & \cc{cvc4} {CVC4} *        \\
    \wc FP           &                          &                           &                                & \cc{cvc4} {CVC4} *        \\

@@

    \wc NIA          & CVC4 \nc{Z3} *           & \cc{prob} ProB \nc{Z3}    & CVC4 \nc{Z3}                   & CVC4 \nc{Z3}              \\

@@

    \wc NRA          & \cc{cvc4} {CVC4} *       & {Vampire}                 & \cc{redl} {Redlog}             & Vampire \nc{Z3} / Vampire \\

@@

    \wc QF\_ANIA     & CVC4 \nc{Z3} *           & {CVC4} *                  & {CVC4} *                       & CVC4 \nc{Z3} *            \\

@@

    \wc QF\_AUFNIA   & {CVC4} *                 & {CVC4} *                  & CVC4 \nc{Z3} *                 & CVC4 \nc{Z3} *            \\

@@

    \wc QF\_BVFP     & \cc{z} {Z3} *            & \wc \nc{Z3} *             & \cc{coli} COLIBRI \nc{Z3} *    & \cc{cvc4} {CVC4}          \\
    \wc QF\_DT       &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4} *        \\

@@

    \wc QF\_FP       & \cc{z} {Z3} *            & \wc \nc{MathSAT} *        & COLIBRI \nc{Z3}                & {COLIBRI}                 \\

@@

    \wc QF\_SLIA     &                          &                           &                                & \cc{cvc4} {CVC4} *        \\

@@

    \wc QF\_UFNIA    & \cc{cvc4} {CVC4} *       & {Yices2/CVC4}             & {Yices2}                       & {Yices2}                  \\

@@

    \wc QF\_UFNRA    & \cc{cvc3} CVC3 \nc{Z3} * & {Yices2}                  & Yices2 \nc{Z3}                 & {Yices2}                  \\

@@

    \wc UFBV         & CVC4 \nc{Z3} *           & CVC4 \nc{Z3}              & CVC4 \nc{Z3} *                 & CVC4 \nc{Z3} *            \\
    \wc UFDT         &                          &                           & \cc{cvc4} {CVC4} *             & \cc{cvc4} {CVC4}          \\
    \wc UFDTLIA      &                          &                           & \cc{vamp} {Vampire} *          & \cc{cvc4} {CVC4}          \\

@@

    \wc UFNIA        & \cc{cvc4} {CVC4} *       & {Vampire}                 & {Vampire}                      & Vampire \nc{Z3} / Vampire \\

>>>>

    \wc ABVFP        &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\

@@

    \wc AUFBVDTLIA   &                              &                           & \nonc \cc{cvc4} {CVC4}          & \nonc \cc{cvc4} {CVC4}    \\
    \wc AUFDTLIA     &                              &                           & \nonc \cc{cvc4} {CVC4}          & \cc{cvc4} {CVC4}          \\

@@

    \wc AUFNIRA      & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & {Vampire}                       & \cc{cvc4} {CVC4}          \\

@@

    \wc BV           & \nonc \cc{cvc4} CVC4 \nc{Z3} & {Q3B}                     & Q3B \nc{Z3}                     & \cc{cvc4} {CVC4}          \\
    \wc BVFP         &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\
    \wc FP           &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\

@@

    \wc NIA          & \nonc CVC4 \nc{Z3}           & \cc{prob} ProB \nc{Z3}    & CVC4 \nc{Z3}                    & CVC4 \nc{Z3}              \\

@@

    \wc NRA          & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & \cc{redl} {Redlog}              & Vampire \nc{Z3} / Vampire \\

@@

    \wc QF\_ANIA     & \nonc CVC4 \nc{Z3}           & \nonc {CVC4}                & \nonc {CVC4}                  & \nonc CVC4 \nc{Z3}        \\

@@

    \wc QF\_AUFNIA   & \nonc {CVC4}                 & \nonc {CVC4}              & \nonc CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}        \\

@@

    \wc QF\_BVFP     & \nonc \cc{z} {Z3}            & \nonc \wc \nc{Z3}         & \nonc \cc{coli} COLIBRI \nc{Z3} & \cc{cvc4} {CVC4}          \\
    \wc QF\_DT       &                              &                           & \nonc \cc{cvc4} {CVC4}          & \nonc \cc{cvc4} {CVC4}    \\

@@

    \wc QF\_FP       & \nonc \cc{z} {Z3}            & \nonc \wc \nc{MathSAT}    & COLIBRI \nc{Z3}                 & {COLIBRI}                 \\

@@

    \wc QF\_SLIA     &                              &                           &                                 & \nonc \cc{cvc4} {CVC4}    \\

@@

    \wc QF\_UFNIA    & \nonc \cc{cvc4} {CVC4}       & {Yices2/CVC4}             & {Yices2}                        & {Yices2}                  \\

@@

    \wc QF\_UFNRA    & \nonc \cc{cvc3} CVC3 \nc{Z3} & {Yices2}                  & Yices2 \nc{Z3}                  & {Yices2}                  \\

@@

    \wc UFBV         & \nonc CVC4 \nc{Z3}           & CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}              & \nonc CVC4 \nc{Z3}        \\
    \wc UFDT         &                              &                           & \nonc \cc{cvc4} {CVC4}          & \cc{cvc4} {CVC4}          \\
    \wc UFDTLIA      &                              &                           & \nonc \cc{vamp} {Vampire}       & \cc{cvc4} {CVC4}          \\

@@

    \wc UFNIA        & \nonc \cc{cvc4} {CVC4}       & {Vampire}                 & {Vampire}                       & Vampire \nc{Z3} / Vampire \\

### 2019-03-20 2018/report/table-winners-unsat-core.tex
Use gray text font instead of * for non-competitive divisions.

    \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c}

@@

    \cc ALIA       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
    \cc AUFBVDTLIA & \cc                            & \cc                                 & CVC4 *                   \\
    \cc AUFLIA     & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
    \cc AUFLIRA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
    \cc AUFNIRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
    \cc BV         & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
    \cc LIA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 \nc{Z3} *           \\
    \cc LRA        & \cc \nc{veriT} *               & CVC4 *                              & CVC4 *                   \\
    \cc NIA        & \cc \nc{Z3} *                  & CVC4 / CVC4 \nc{Z3}*                & CVC4 *                   \\
    \cc NRA        & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
    \cc QF\_ABV    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & Yices2                   \\
    \cc QF\_ABVFP  & \cc                            & \cc ---                             & \cc CVC4 *               \\
    \rc
    \cc QF\_ALIA   & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & Yices2 \nc{Z3}           \\
    \cc QF\_ANIA   & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
    \rc
    \cc QF\_AUFBV  & \nc{Z3} *                      & CVC4 \nc{MathSAT} *                 & Yices2 \nc{MathSAT}      \\
    \cc QF\_AUFLIA & \cc SMTInterpol \nc{Z3} *      & CVC4                                & CVC4                     \\
    \cc QF\_AUFNIA & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
    \drc
    \cc QF\_AX     & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
    \rc
    \cc QF\_BV     & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2                   \\
    \cc QF\_BVFP   & \nc{Z3} *                      & \nc{Z3} *                           & \cc CVC4 \nc{Z3} *       \\
    \rc
    \cc QF\_DT     &                                &                                     & CVC4 *                   \\
    \rc
    \cc QF\_FP     & \nc{MathSAT} *                 & \nc{Z3} *                           & CVC4 *                   \\
    \cc QF\_IDL    & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
    \drc
    \cc QF\_LIA    & SMTInterpol \nc{Z3} *          & SMTInterpol / SMTInterpol \nc{Z3}   & SMTInterpol              \\
    \cc QF\_LIRA   & \cc SMTInterpol \nc{Z3} *      & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
    \drc
    \cc QF\_LRA    & SMTInterpol *                  & SMTInterpol                         & SMTInterpol              \\
    \cc QF\_NIA    & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
    \cc QF\_NIRA   & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
    \cc QF\_NRA    & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
    \cc QF\_RDL    & \cc SMTInterpol \nc{veriT} *   & CVC4 \nc{Z3}                        & CVC4 \nc{Z3}             \\
    \cc QF\_UF     & \cc SMTInterpol \nc{MathSAT} * & CVC4                                & CVC4                     \\
    \rc
    \cc QF\_UFBV   & \nc{MathSAT} *                 & CVC4 \nc{MathSAT} *                 & Yices2 \nc{Z3}           \\
    \drc
    \cc QF\_UFIDL  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{Z3}                 & \cc Yices2               \\
    \drc
    \cc QF\_UFLIA  & SMTInterpol \nc{MathSAT} *     & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}      \\
    \drc
    \cc QF\_UFLRA  & SMTInterpol \nc{Z3} *          & SMTInterpol \nc{MathSAT}            & \cc Yices2 \nc{MathSAT}  \\
    \cc QF\_UFNIA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
    \cc QF\_UFNRA  & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
    \cc UF         & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
    \cc UFBV       & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 *                   \\
    \rc
    \cc UFDT       &                                &                                     & CVC4 *                   \\
    \cc UFIDL      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
    \cc UFLIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\
    \cc UFLRA      & \cc \nc{Z3} *                  & CVC4 \nc{Z3} *                      & CVC4 \nc{Z3} *           \\
    \cc UFNIA      & \cc \nc{Z3} *                  & CVC4 *                              & CVC4 *                   \\

>>>>

    \begin{tabular}{r@{\hskip 1em}>{\nonc \columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c}

@@

      \rc{cvc4}
      \wc ALIA       & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
      \wc AUFBVDTLIA &                                     &                                   & \nonc \cc{cvc4} CVC4           \\
      \rc{cvc4}
      \wc AUFLIA     & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4                     \\
      \rc{cvc4}
      \wc AUFLIRA    & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4                     \\
      \rc{cvc4}
      \wc AUFNIRA    & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
      \rc{cvc4}
      \wc BV         & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
      \rc{cvc4}
      \wc LIA        & \wc \nc{veriT}                      & \nonc CVC4                        & \nonc CVC4 \nc{Z3}             \\
      \rc{cvc4}
      \wc LRA        & \wc \nc{veriT}                      & \nonc CVC4                        & \nonc CVC4                     \\
      \rc{cvc4}
      \wc NIA        & \wc \nc{Z3}                         & \nonc CVC4 / CVC4 \nc{Z3}         & \nonc CVC4                     \\
      \rc{cvc4}
      \wc NRA        & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
      \wc QF\_ABV    & \wc \nc{Z3}                         & \nonc \cc{cvc4} CVC4 \nc{Z3}      & \cc{yices} Yices2              \\
      \wc QF\_ABVFP  &                                      & ---                              & \nonc \cc{cvc4} CVC4           \\
      \rc{smti}
      \wc QF\_ALIA   & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}               & \cc{yices} Yices2 \nc{Z3}      \\
      \rc{cvc4}
      \wc QF\_ANIA   & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
      \wc QF\_AUFBV  & \nc{Z3}                             & \nonc \cc{cvc4} CVC4 \nc{MathSAT} & \cc{yices} Yices2 \nc{MathSAT} \\
      \rc{cvc4}
      \wc QF\_AUFLIA & \cc{smti} SMTInterpol \nc{Z3}       & CVC4                              & CVC4                           \\
      \rc{cvc4}
      \wc QF\_AUFNIA & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
      \rc{smti}
      \wc QF\_AX     & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}               & \cc{yices} Yices2              \\
      \wc QF\_BV     & \nc{MathSAT}                        & \nonc \cc{cvc4} CVC4 \nc{MathSAT} & \cc{yices} Yices2              \\
      \wc QF\_BVFP   & \nc{Z3}                             & \nonc \nc{Z3}                     & \nonc \cc{cvc4} CVC4 \nc{Z3}   \\
      \wc QF\_DT     &                                     &                                   & \nonc \cc{cvc4} CVC4           \\
      \wc QF\_FP     & \nc{MathSAT}                        & \nonc \nc{Z3}                     & \nonc \cc{cvc4} CVC4           \\
      \rc{cvc4}
      \wc QF\_IDL    & \cc{smti} SMTInterpol \nc{Z3}       & CVC4 \nc{Z3}                      & CVC4 \nc{Z3}                   \\
      \rc{smti}
      \wc QF\_LIA    & SMTInterpol \nc{Z3}                 & SMTInterpol / SMTInterpol \nc{Z3} & SMTInterpol                    \\
      \rc{cvc4}
      \wc QF\_LIRA   & \cc{smti} SMTInterpol \nc{Z3}       & CVC4 \nc{Z3}                      & CVC4 \nc{Z3}                   \\
      \rc{smti}
      \wc QF\_LRA    & SMTInterpol                         & SMTInterpol                       & SMTInterpol                    \\
      \rc{cvc4}
      \wc QF\_NIA    & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
      \rc{cvc4}
      \wc QF\_NIRA   & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
      \rc{cvc4}
      \wc QF\_NRA    & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
      \rc{cvc4}
      \wc QF\_RDL    & \cc{smti} SMTInterpol \nc{veriT}    & CVC4 \nc{Z3}                      & CVC4 \nc{Z3}                   \\
      \rc{cvc4}
      \wc QF\_UF     & \cc{smti} SMTInterpol \nc{MathSAT}  & CVC4                              & CVC4                           \\
      \wc QF\_UFBV   & \nc{MathSAT}                        & \nonc \cc{cvc4} CVC4 \nc{MathSAT} & \cc{yices} Yices2 \nc{Z3}      \\
      \rc{smti}
      \wc QF\_UFIDL  & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{Z3}               & \cc{yices} Yices2              \\
      \rc{smti}
      \wc QF\_UFLIA  & SMTInterpol \nc{MathSAT}            & SMTInterpol \nc{Z3}               & SMTInterpol \nc{Z3}            \\
      \rc{smti}
      \wc QF\_UFLRA  & SMTInterpol \nc{Z3}                 & SMTInterpol \nc{MathSAT}          & \cc{yices} Yices2 \nc{MathSAT} \\
      \rc{cvc4}
      \wc QF\_UFNIA  & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
      \rc{cvc4}
      \wc QF\_UFNRA  & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
      \rc{cvc4}
      \wc UF         & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
      \rc{cvc4}
      \wc UFBV       & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4                     \\
      \wc UFDT       &                                     &                                   & \nonc \cc{cvc4} CVC4           \\
      \rc{cvc4}
      \wc UFIDL      & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
      \rc{cvc4}
      \wc UFLIA      & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
      \rc{cvc4}
      \wc UFLRA      & \wc \nc{Z3}                         & \nonc CVC4 \nc{Z3}                & \nonc CVC4 \nc{Z3}             \\
      \rc{cvc4}
      \wc UFNIA      & \wc \nc{Z3}                         & \nonc CVC4                        & \nonc CVC4                     \\
